---
title: "AEX investment App"
author: "Bert Ypey"
date: "11 oktober 2019"
output:
  slidy_presentation: default
runtime: shiny
---


# <span style="color:purple">Introduction</span>

<font size="6">
`This application supports Investment decisions in stocks listed at the Amsterdam Stock Exchange(AEX)` <br>
`The application downloads the stocks of which the Amsterdam Stock Exchange is composed` <br><br>
`Stock and Index Data is downloaded from the Yahoo Finance site, using the getSymbols command.`
</font>


# <span style="color:purple">AEX Stocks</span>

```{r echo=FALSE, results="hide", message=FALSE, warning=FALSE}
library(htmltab)
library(kableExtra)
tabledata.url <- "https://en.wikipedia.org/wiki/AEX_index"
AEX.components = htmltab(doc = tabledata.url, which=2, rm_nodata_cols = F)

#colnames(AEX.components)[colnames(AEX.components)=="Ticker symbol"] <- "Ticker"
#colnames(AEX.components)[colnames(AEX.components)=="Index weighting (%)"] <- "Index weight(perc)"
#AEX.components

AEXdf <- data.frame(AEX.components)

Output <- AEXdf %>% kable(col.names=c("Company", "Industry sector", "Ticker symbol", "Index weight (%)")) %>% kable_styling(bootstrap_options = "striped", full_width = F)

```   

```{r}
Output
```

# <span style="color:purple">Input and Output App</span>



- As input a choice is given in a dropdown menu to choose the stock to investigate

- A slide bar can be used to specify the range of data to zoom in on

- As output 4 tabs are given
    - Table :containing the starting stockprice and last stockprice requested
    - Performance: Graph showing performance over chosen timeframe of stock against AEX index
    - Stockplot including moving average data and standard deviation data
    - Normalized graph: Comparing the stock price development versus the AEX index



# <span style="color:purple">Example output App</span>

```{r echo=FALSE, results="hide", message=FALSE, warning=FALSE}
library(shiny)

## Initialization
library(htmltab)
library(plotly)
{## get AEX components names

        tabledata.url <- "https://en.wikipedia.org/wiki/AEX_index"
        AEX.components = htmltab(doc = tabledata.url, which=2, rm_nodata_cols = F)
        AEX.components.Symbol = paste0(AEX.components[['Ticker symbol']], '.AS')
        names(AEX.components.Symbol) =  paste0( AEX.components[['Company']], ' (', AEX.components[['ICB Sector']] ,')' )

}



#p("This app shows the performance of a particular AEX stock in comparison with the AEX index"),

# Define UI for dataset viewer application
ui <- shinyUI(fluidPage(

        # Application title
        headerPanel("AEX stock performance vs AEX"),
        p("This app shows the performance of a particular AEX stock in comparison with the AEX index."),
        p("The Sidebar shows a drop panel in which a stock can be selected and a sliderinput to specify the data range to view."),
        p("The Main Panel includes 4 tabs to view the results."),

        sidebarLayout(

                # Sidebar with controls to select a dataset and specify the number
                # of observations to view. The helpText function is also used to
                # include clarifying text. Most notably, the inclusion of a
                # submitButton defers the rendering of output until the user
                # explicitly clicks the button (rather than doing it immediately
                # when inputs change). This is useful if the computations required
                # to render output are inordinately time-consuming.
                sidebarPanel(

                        selectInput("stock_id", "AEX Stock:",
                                    AEX.components.Symbol),

                        # textInput("stock_id", "Type in stock ID to fetch data from Yahoo", e.g. "AALB.AS"),

                        # Specification of range within an interval
                        helpText("Specify Range (in % of data)"),
                        sliderInput("range", "Range:",
                                    min = 0, max = 100, value = c(0,100)),

                        helpText("Load Stockdata from Yahoo")

                        # submitButton("Update View")
                ),

                # Show a hierarchy of panels with plots
                mainPanel(

                        tabsetPanel(
                                tabPanel(
                                        "Table",
                                        tableOutput("tablehead"),
                                        tableOutput("tabletail"),
                                        p("AEX and stock data at beginning and end of range,")
                                ),

                                tabPanel(
                                        "Performance",
                                        plotOutput("timeseries"),
                                        p("The top chart is a normal cumulative return or wealth index chart that shows the
cumulative returns through time for each column."),
                                        p("The second chart shows the individual daily returns"),
                                        p("The third chart in the series is a drawdown or underwater chart, which shows the level
of losses from the last value of peak equity attained.")
                                ),

                                tabPanel("Stockplot",
                                         p("Stockprice over time with moving average data"),
                                         plotOutput("stockplot"),
                                         p("Use the Range slider to zoom in on specific time periods."),
                                         p("Bolingerband gives the range between the 14 days moving average and twice the standarddeviation.")

                                ),



                                tabPanel("Normalized graph", p("Normalized plot with index set at 100 at starting date."),
                                         plotlyOutput("normalizedplot"),
                                p("In some cases the stock graph does not appear,"),
                                p("in which case there is no stock data is available at the beginning of the chosen data range"),
                                p("In that case slide the range further to the right")
                                )

                        )

                )
        )))

#
library(shiny)
library(quantmod)
library(PerformanceAnalytics)
library(plotly)


## Intialize AEX data
AdjustedPrice = 6
AEXall = getSymbols('^AEX', warnings = FALSE, auto.assign = FALSE)
AEX = na.fill(AEXall, fill = "extend")[,AdjustedPrice, drop=FALSE]


# Define server logic required to summarize and view the selected dataset
server <- shinyServer(function(input, output, session) {

        # Return the requested dataset
        datasetInput <- reactive({


                stockdataall = getSymbols(input$stock_id, warnings = FALSE, auto.assign = FALSE)
                stockdata = na.fill(stockdataall, fill = "extend")[, AdjustedPrice, drop=FALSE]

                stockdata = merge (AEX, stockdata)

                no_of_datapoints = dim(stockdata)[1]

                min = input$range[1]/100 * no_of_datapoints
                max = input$range[2]/100 * no_of_datapoints

                # AdjustedPrice

                #out = stockdata
                out = stockdata[min:max,]

                return (out)
        })

        # generate a table
        output$tablehead <- renderTable({
                table <- data.frame(datasetInput())
                table$date <- rownames(table)
                table <- table[,c(3,1,2)]
                head(table,5)

        })

        # generate a table
        output$tabletail <- renderTable({
                table <- data.frame(datasetInput())
                table$date <- rownames(table)
                table <- table[,c(3,1,2)]
                tail(table,5)

        })

        # generate a plot
        output$timeseries <- renderPlot({

                AdjustedPrice <- datasetInput()


                Returns <- AdjustedPrice/lag(AdjustedPrice, 1) -1 # daily returns
                charts.PerformanceSummary(Returns)

        })



        # generate a plot
        output$stockplot <- renderPlot({

                #stockdataall1 = getSymbols(input$stock_id, warnings = FALSE, auto.assign = FALSE)
                #Index <- stockdataall1[,6]

                Index <- datasetInput()
                Index <- data.frame(Index)
                Index$datum <- as.Date(row.names(Index))

                Index <- na.locf(Index)
                colnames(Index)[2]<- "Index"
                Index$MA10 <- SMA(Index$Index, n=10)
                Index$MA20 <- SMA(Index$Index, n=20)
                Index$MA50 <- SMA(Index$Index, n=50)
                Index$MA200 <- SMA(Index$Index, n=200)
                #Index$RSI <- RSI(Index$Index, n=14)

                library(roll)
                summary(Index)
                sd(Index$Index,100)

                MATRIX <- matrix(Index$Index)
                Index$RollSD<-roll_sd(MATRIX,20, complete_ob = TRUE)

                Index$Bollingerplus <- Index$MA20+2*Index$RollSD
                Index$Bollingermin <- Index$MA20-2*Index$RollSD

                graph = ggplot()

                graph = graph + geom_line(data=Index, aes(x=datum, y=Index, group=1, colour="Index"))

                graph = graph + geom_line(data=Index, aes(x=datum, y=MA20,  group=1, colour="MA20"))
                graph = graph + geom_line(data=Index, aes(x=datum, y=MA50,  group=1, colour="MA50"))
                graph = graph + geom_line(data=Index, aes(x=datum, y=MA200,  group=1, colour="MA200"))

                graph = graph + geom_ribbon(data=Index, aes(x=datum, ymin=Bollingermin, ymax=Bollingerplus, fill="Bollingerband"), alpha="0.2")

                graph = graph + scale_x_date(breaks = function(x) seq.Date(from = min(x), to=max(x), by = "1 year"))

                graph = graph + theme(axis.text.x=element_text(angle = 45, hjust=1)) +ylab("index")

                graph
        })




        # generate a plot
        output$normalizedplot <- renderPlotly({

                table <- data.frame(datasetInput())
                table$date <- rownames(table)
                table <- table[,c(3,1,2)]
                stock <- input$stock_id

                x <- list( title="date", showgrid = T , zeroline = F , nticks = 20 , showline = T)
                y <- list( title="Normalized Index", showgrid = T , zeroline = F , nticks = 20 , showline = T)

                p=plot_ly(table, x = ~date, y = 100*table[,2]/table[,2][2], type = "scatter", mode = "lines", name="AEX") %>%
                       layout(title="Normalized plot", xaxis=x, yaxis=y)

                p = add_lines(p, x=~date, y=100*table[,3]/table[,3][2], name=stock)

                p


        })

})

```

```{r}
shinyApp(ui = ui, server = server)

```

